% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
% {{{ setup
\documentclass[a4paper]{article}

\newcommand*{\ShowReferences}{} % Comment to hide the References.
%\newcommand*{\ShowGlossary}{} % Comment to hide the Glossary.

\newcommand{\doctitle}{Boring Flops}

\usepackage[pdftex,pdfauthor={Dave McEwan},pdftitle={\doctitle},breaklinks,hidelinks]{hyperref}

\input{shr/tex/setupGeneric.tex}

% }}} setup

\begin{document}
% {{{ prolog

\title{
  \doctitle
}

\author{
  Dave M\textsuperscript{c}Ewan\orcidID{0000-0002-1125-2022}
}

\maketitle

\begin{abstract}
\TODO{Abstract}
\end{abstract}

% }}} prolog

\section{Introduction} % {{{
\label{sec:introduction}
\TODO{Introduction}

\subsection{Problem Description} % {{{
\label{sec:problem}
\TODO{Problem Description}

% }}} sec:problem

\subsection{Objective} % {{{
\label{sec:objective}
\TODO{Objective}

% }}} sec:objective

\subsection{Approach} % {{{
\label{sec:approach}
\TODO{Approach}

% }}} sec:approach

% }}} sec:introduction

\section{Background and Related Work} % {{{
\label{sec:background}
\TODO{Background}

% }}} sec:background

\section{Methodology} % {{{
\label{sec:methodology}
\TODO{Methodology}

% }}} sec:methodology

\section{Discussion} % {{{
\label{sec:discussion}
\TODO{Discussion}

\subsection{Worked Example} % {{{
\label{sec:workedExample}
\TODO{Worked Example}

% }}} sec:workedExample

\subsection{Tool Support} % {{{
\label{sec:toolSupport}
These selected \gls{FOSS} and commercial tools have been specifically tested,
and examples of their usage is contained in \texttt{dmpvl/mk/lint.mk}.
Full support is provided by all modern tools when the appropriate flags are
used for System Verilog mode.
Only the oldest tested version of each tool is shown because no regressions
have been seen in newer versions.

% TODO: Tidy up description style.
\begin{description}
\item[Icarus, AKA iverilog (\gls{FOSS})]
  Simulator.
  Specific flag (\texttt{-E}) allows enables use as a standalone pre-processor.
\item[Verilator (\gls{FOSS})]
  Fast, 2-state simulator.
  Specific flag (\texttt{-E}) allows enables use as a standalone pre-processor.
\item[Yosys - (\gls{FOSS})]
  Generic synthesis tool primarily targeting Lattice and Xilinx \glspl{FPGA}.
\item[HAL 20.03 (Cadence)]
  Linter.
\item[JasperGold 2020.03 (Cadence)]
  Formal proof assistant.
\item[Xcelium 20.03 (Cadence)]
  Simulator.
\item[Formalpro v2020.1 (Siemens)]
  Equivalence checker.
\item[Design Compiler TODO (Synopsys)]
  Generic synthesis tool for \glspl{ASIC}.
  \TODO{Full support for \gls{DFF} macros.???}
\item[Spyglass 2020.12 (Synopsys)]
  Linter.
\item[VCS 2018.09 (Synopsys)]
  Simulator.
\item[Vivado 2018.02 (Xilinx)]
  Complete \gls{FPGA} flow including synthesis (Synplify Pro) and simulation.
\end{description}

% }}} sec:toolSupport

\subsection{Potential Problems} % {{{
\label{sec:potentialProblems}
\TODO{Potential Problems}

% }}} sec:potentialProblems

% }}} sec:discussion

\section{Conclusion} % {{{
\label{sec:conclusion}
\TODO{Conclusion}

% }}} sec:conclusion

% {{{ epilog

\ifdefined\ShowReferences
  \newpage
  \bibliographystyle{shr/tex/IEEEtran}
  \bibliography{shr/refs}{} % refs.bib
\fi

\ifdefined\ShowGlossary
  \clearpage
  \phantomsection
  \addcontentsline{toc}{section}{Glossary}
  \printnoidxglossary[sort=letter]
\fi

% }}} epilog

\end{document}
